---
title: '228 Practicum 2: Measurement'
author: "Molly Williams"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Monterey Bay Seafood Watch (SFW): Understanding Program Influence Across Targeted Sectors
**According to their theory of change, the SFW prgram seeks to improve the sustainability of global fisheries and aquaculture operations by assigning ratings to these entities and promoting knowledge of them to businesses and consumers.**

### We design sampling strategies for three of the measures used to determine the impact of the SFW program:
1. Assess likelihood of changes in consumer behavior as a result of engagement with SFW guides
2. Business engagement with program and effeciveness of business partnerships
3. Changes in practices of fisheries, aquaculture operations, NGOs and/or governments that are given red ratings



#### 0. Load required packages: 
```{r}
library(DeclareDesign)
library(knitr)
library(ggplot2)
library(grid)
library(gridExtra)
library(dplyr)
library(kableExtra)
library(tidyverse)

```

### Sampling strategies 

#### 1. Assess likelihood of changes in consumer behavior as a result of engagement with SFW guides

*Survey question*: How likely are you to make different seafood purchasing decisions based on your use of the SFW Guide? 
a) Very Likely
b) Likely
c) Somewhat Likely
d) Not at all likely

*Target Population*: Seafood consumers who use the paper guides, the app, or the website to inform their purchasing decisions

*Declaring the population:* According to the SFW website, they have distributed more than 57 million paper guides, and have logged over 1.8 million app downloads. They do not make publicly available the number of hits they get on their website. 

*Challenge of drawing a representative sample*: Users may be more willing to complete a survey within the app or on the web platform with a popup than they are to complete a survey based on a link at the back of a paper guide. Even though there are more paper user guides distributed than app downloads, we expect more app users than paper guide users to respond to the survey, so we weight the two equally. 

*Hypothetical population*:
```{r}
pop.vector <- c(5700,180) # Number of paper guides distributed and app downloads, respectively, in tens of thousands 

set.seed(228)
population <- declare_population(
  platform = add_level(N=2,
         baseline=c(0.5,0.5)), # We estimate that 50% of people who interact with SFW materials change behavior, no matter the platform
  respondents = add_level(N=pop.vector,
                          e=rnorm(n=sum(pop.vector)),
                          behavior=draw_ordered(baseline+e,
                                                breaks = c(-Inf,-1, 0, 0.5, Inf))))

pop <- population()
table(pop$behavior)

# 1 = Very Likely
# 2 = Likely
# 3 = Somewhat Likely
# 4 = Not at all likely

my_estimand <- declare_estimands(mean(behavior),
                                 label = "Ybar")
my_estimand(pop)

```

*Reporting probabilities and sampling procedures*: Cluster-based sampling across each platform with unequal effort according to potential sample size.
```{r}

# We expect 5% of paper guide users to respond to a survey vs. 10% of app/web users
reporting <- declare_assignment(blocks=platform, block_prob=c(0.05, 0.1),
                  assignment_variable = "R")
rep <- reporting(pop)

# Determine the number of surveys to administer based on a goal of collecting 1000 surveys, with 500 from each group
sampling <- declare_sampling(strata=platform,
               strata_n=c(200, 100))

```

*Estimate declared population*: 
```{r}

strata_weighted_mean <- function(data){
  data.frame(  
  estimator_label = "strata_w_mean",
  estimand_label = "Ybar",
  n = nrow(data),
  stringsAsFactors = FALSE,
  
  estimate = data %>% filter(R==1) %>%
    group_by(platform) %>% 
    summarise(mean=mean(behavior)) %>%
    mutate(prop=pop.vector/sum(pop.vector)) %>%
    mutate(sub.mean=mean*prop) %>% pull(sub.mean) %>% 
    sum())
}


```

*Create table for standard deviations*
```{r}

answer <- declare_estimator(
  handler = tidy_estimator(strata_weighted_mean),
  estimand = my_estimand)

design <- population + my_estimand + reporting +
          sampling + answer

diagnosis <- diagnose_design(design, sims = 100)

diagnosis$diagnosands_df[,c(4,5,12,14)] %>%
  kable()

```


#### 2. Partner engagement with program and effeciveness of conservation partnerships (#6 and #8 in measures)

*Survey question*: Did you acquire this guide/hear about it from a zoo, aquarium, or museum?
a) Yes
b) No


*Target Population*: Seafood consumers who use the paper guides, the app, or the website to inform their purchasing decisions

*Declaring the population:* According to the SFW website, they have distributed more than 57 million paper guides, and have logged over 1.8 million app downloads. They do not make publicly available the number of hits they get on their website, and they do not report the number of guides that are distributed or recommended by business partners (food retailers, restaurants, and conservation partners such as zoos, museums and aquariums).

*Challenge of drawing a representative sample*: Users may be more willing to complete a survey within the app or on the web platform with a popup than they are to complete a survey based on a link at the back of a paper guide. Even though there are more paper user guides distributed than app downloads, we expect more app users than paper guide users to respond to the survey, so we weight the two equally. 

*Hypothetical population*:
```{r}

pop.vector <- c(5700,180) # Number of paper guides distributed and app downloads, respectively, in tens of thousands 

set.seed(228)
population2 <- declare_population(
  platform2 = add_level(N=2,
         baseline2=c(0.8,0.2)), # We estimate that 80% of people who interact with SFW materials learned about the program from a conservation partner (zoos, aquariums, museums).
  respondents = add_level(N=pop.vector,
                          e=rnorm(n=sum(pop.vector)),
                          behavior2=draw_binary(baseline2))) # no breaks assigned here because we are using binary

pop2 <- population2()
table(pop2$behavior)

# 0 = Yes, acquired information about the program from a conservation partner
# 1 = No, did not hear about the program from a conservation partner


my_estimand2 <- declare_estimands(mean(behavior2),
                                 label = "Ybar")

my_estimand2(pop2) # 0.77



```

*Reporting probabilities and sampling procedures*: Cluster-based sampling across each platform with unequal effort according to potential sample size.
```{r}

# We expect 5% of paper guide users to respond to a survey vs. 10% of app/web users
reporting2 <- declare_assignment(blocks=platform2, block_prob=c(0.05, 0.1),
                  assignment_variable = "R")

# Determine the number of surveys to administer based on a goal of collecting 1000 surveys
sampling2 <- declare_sampling(strata=platform2,
               strata_n=c(200, 100))

```

*Estimate declared population*: 
```{r}

strata_weighted_mean2 <- function(data){
  data.frame(  
  estimator_label = "strata_w_mean",
  estimand_label = "Ybar",
  n = nrow(data),
  stringsAsFactors = FALSE,
  
  estimate = data %>% 
    filter(R==1) %>%
    group_by(platform2) %>% 
    summarise(mean=mean(behavior2)) %>%
    mutate(prop=pop.vector/sum(pop.vector)) %>%
    mutate(sub.mean=mean*prop) %>% pull(sub.mean) %>% 
    sum())
}


```

*Create table for standard deviations*
```{r}

answer2 <- declare_estimator(
  handler = tidy_estimator(strata_weighted_mean2),
  estimand = my_estimand2)

design2 <- population2 + my_estimand2 + reporting2 +
          sampling2 + answer2

diagnosis2 <- diagnose_design(design2, sims = 100) 

diagnosis2$diagnosands_df[,c(4,5,12,14)] %>%
  kable()

# estimate is 0.757; close to initial estimand of 0.774

```



#### 3. Will yellow- and red-rated operations approach SFW for guidance in order to improve their rating?

According to the SFW theory of change, seafood production operations (e.g. fisheries, aquaculture operations, NGOs and/or governments) that receive a yellow or red rating will seek guidance from the program in order to improve their practices and subsequently their rating. However, SFW has expressed that potential roadblocks exist for operations to improve their ratings, and they have an active interest in understanding what these are and how they can be addressed. In this example we use the West Coast SFW guide as a case study for predicting operations' responses after they are given an unfavorable rating. (#7 in measures list) 


*Survey question*: After receiving your rating, do you plan to seek guidance from SFW on how you can improve your rating? a) Yes
b) No

*Target Population*: Leaders of fisheries, aquaculture operations, NGOs and/or governments that are given red or yellow ratings

*Declaring the population:* The West coast SFW guide lists 17 yellow-rated ("good alternative", e.g. US wild oysters) and 21 red-rated ("avoid") fisheries (e.g. bluefin tuna), which each contain an unknown number of individual operations. We use a conservative estimate of 50 operations for each fishery to get a total of 850 yellow-rated and 1050 red-rated operations that can be surveyed.

*Challenge of drawing a representative sample*: Certain fisheries or operations are more willing to reach out for assistance if they are more interested in changing their practices. Operations that received a yellow rating may be more likely to respond as they theoretically have less work to do to . THis may result in red-rated operations having a lower response rate overall. We assume that the companies that do reach out will have evidence or belief that improving their ratings will have a positive effect on their business outcomes and that retaining a red rating will result in negative business outcomes.

*Hypothetical population*:
```{r}

pop.vector3 <- c(850, 1050) # estimated number of yellow- and red-rated operations in the US West Coast Guide, respectively

set.seed(228)
population3 <- declare_population(
  rating = add_level(N=2,
         baseline3=c(0.3,0.2)), # We estimate that 30% of operations with yellow ratings and 20% with red ratings will approach SFW for guidance on how to change their practices
  operations = add_level(N=pop.vector3,
                         e=rnorm(n=sum(pop.vector3)),
                         behavior3=draw_binary(baseline3)))

pop3 <- population3()
table(pop3$behavior)

# 0 = Will not come to SFW for guidance
# 1 = Will come to SFW for guidance 

my_estimand3 <- declare_estimands(mean(behavior3),
                                 label = "Ybar")

my_estimand3(pop3) # 0.241


```

*Reporting probabilities and sampling procedures*: Cluster-based sampling across each platform with unequal effort according to potential sample size.
```{r}

# We expect 15% of yellow-rated operations to respond to a survey vs. 10% of red-rated operations
reporting3 <- declare_assignment(blocks=rating, block_prob=c(0.15, 0.1),
                  assignment_variable = "R")

# Determine the number of surveys to administer based on a goal of collecting 100 surveys
sampling3 <- declare_sampling(strata=rating,
               strata_n=c(100, 200))

```

*Estimate declared population*: 
```{r}

strata_weighted_mean3 <- function(data){
  data.frame(  
  estimator_label = "strata_w_mean",
  estimand_label = "Ybar",
  n = nrow(data),
  stringsAsFactors = FALSE,
  
  estimate = data %>% 
    filter(R==1) %>%
    group_by(rating) %>% 
    summarise(mean=mean(behavior3)) %>%
    mutate(prop=pop.vector3/sum(pop.vector3)) %>%
    mutate(sub.mean=mean*prop) %>% pull(sub.mean) %>% 
    sum())
}


```

*Create table for standard deviations*
```{r}

answer3 <- declare_estimator(
  handler = tidy_estimator(strata_weighted_mean3),
  estimand = my_estimand3)

design3 <- population3 + my_estimand3 + reporting3 +
          sampling3 + answer3

diagnosis3 <- diagnose_design(design3, sims = 100)

diagnosis3$diagnosands_df[,c(4,5,12,14)] %>%
  kable()

```

