---
title: '228 Practicum 3: Impact Evaluation'
author: "Danny Elkin, Eric Holmes, Molly Williams"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### 0. Load required packages: 
```{r message=FALSE}
library(DeclareDesign)
library(truncnorm)
library(knitr)
library(tidyverse)

```


## Declare population

```{r}
set.seed(101)
population <- declare_population(
  restaurant = add_level(N=700, # is this total or just those assigned to treatment group?
    baseline = rtruncnorm(n=N, a=0.38, b=8.21,
                          mean=1.2, sd=2), # what would be a reasonable range here
    annual_change_rate = rnorm(n=N, mean=1.1, sd=0.2))
)

# what does changing runif() to rtruncnorm() do?

pop <- population()

```


## Declare potential outcomes

```{r}

potential_outcomes <-
declare_potential_outcomes(
Y_Z_0 = baseline * annual_change_rate,
Y_Z_1 = baseline * annual_change_rate * 0.9) # why do we multiply by 0.9?
po <- potential_outcomes(pop)


```


## Potential outcomes descriptives 

```{r}

```{r po-see, echo=FALSE}
kable(po[1:5,], digits=1)
```

```{r po-check, echo=TRUE}
mean(po$baseline)
sd(po$baseline) # want this to match your baseline distribution?

```


## Declare sample size
```{r}
sampling <- declare_sampling(n=700) # again, is this the treatment group or the total number of samples?
sam <- sampling(po)
```


## Declare treatment assignment and reveal potential outcomes
```{r}

# Assign half the units to the treatment group
assigning <- declare_assignment(prob=0.5)
assigned <- assigning(sam)
kable(assigned[1:5,c(1:2,4:5,7)],
digits = 1)


# Declare  how the potential outcomes are revealed by the random assignment
revealing <- declare_reveal()

```


## Declare estimand and estimator

```{r}

# what is our target treatment effect?

estimand <- declare_estimand(
prop.change = mean((Y_Z_1-Y_Z_0)/baseline))
estimand(po) # 10% decrease in WQI in this example

# really not sure what this does... how does it incorporate desired treatment effect?
dip <- declare_estimator(Y*(1/baseline) ~ Z,
estimand = estimand,
model = lm_robust, label = "DIP")
```

## Declare and diagnose design
```{r}
design <- population + potential_outcomes + sampling +
assigning + revealing + estimand + dip

diagnosis <- diagnose_design(design)
diagnosis$diagnosands_df[,c(1,3,5,9,11)] %>% # selecting only certain columns?
kable()

# Visualize estimates 
hist(diagnosis$simulations_df$estimate)

```

## Levers
### How do we know which one to use? Blocking or increase sample size? Should we just start with this initially in our design? 


